Higher-Order unification for free!

### 2024-05-13 paper/main.tex
[fh]variable renamed to [om]variable

\noindent
Each \elpiIn{hvariable} is stored in the mapping together with
its arity (a number) so that the code of \ref{clause:malloc} below can preserve:

@@

\noindent
When a single \elpiIn{fvariable} occurs multiple times with different numbers
of arguments, the compiler generates multiple mappings for it, on a first
approximation, and then ensures the mapping are bijective by introducing
\linketa; this detail is discussed in section \ref{sec:invariant1}.

>>>>

\noindent
Each \elpiIn{mvariable} is stored in the mapping together with
its arity (a number) so that the code of \ref{clause:malloc} below can preserve:

@@

\noindent
When a single \elpiIn{ovariable} occurs multiple times with different numbers
of arguments, the compiler generates multiple mappings for it, on a first
approximation, and then ensures the mapping are bijective by introducing
\linketa; this detail is discussed in section \ref{sec:invariant1}.
